Model matters with restricted Boltzmann machines

### 2019-11-20 presentations/silo_wisc/slides.Rmd
update slides

>>>>

# Avoiding S-instability for the RBM

Based on the definition of S-instability, we can show how an S-unstable distribution can arise (and potentially how to avoid this).

- All instability in the marginal RBM model for the data $\boldsymbol X$ can be attributed to large magnitudes (or many terms) of $\boldsymbol \theta_{v}$ and/or $\boldsymbol \theta_{interaction}$
- An S-unstable marginal model implies an S-unstable joint model
- Further potential causes of S-instability exist for the joint model, often due to the size of $|\boldsymbol \theta_{v}|_1$

#### Key Finding
To prevent instability in the joint model of an RBM (and all models that embloy RBMs, e.g. a DBM), the combined magnitudes of all parameters $\boldsymbol \theta$ must be controlled.

### 2019-11-20 presentations/silo_wisc/slides.tex
update slides

>>>>

\begin{frame}{Avoiding S-instability for the RBM}
\protect\hypertarget{avoiding-s-instability-for-the-rbm}{}

Based on the definition of S-instability, we can show how an S-unstable
distribution can arise (and potentially how to avoid this).

\begin{itemize}
\tightlist
\item
  All instability in the marginal RBM model for the data
  \(\boldsymbol X\) can be attributed to large magnitudes (or many
  terms) of \(\boldsymbol \theta_{v}\) and/or
  \(\boldsymbol \theta_{interaction}\)
\item
  An S-unstable marginal model implies an S-unstable joint model
\item
  Further potential causes of S-instability exist for the joint model,
  often due to the size of \(|\boldsymbol \theta_{v}|_1\)
\end{itemize}

\begin{block}{Key Finding}

To prevent instability in the joint model of an RBM (and all models that
embloy RBMs, e.g.~a DBM), the combined magnitudes of all parameters
\(\boldsymbol \theta\) must be controlled.
